Tropical mathematics and the Lambda-calculus I

### 2023-08-02 CSL24/main.tex
Commit

\section{Proofs from \autoref{section22}: $(\LREL, !_{n})$ is a model of $\BSTLC$}
\input{appSection5}

\section{Proofs from \autoref{sec:tls}}\label{appsec:tls}
%\input{app_section4}

\section{Proofs from \autoref{sec:TayLip}: $\Lawv$-modules and Generalized Metric Spaces}
\input{appSection7}

\section{Proofs of \autoref{sec:GMS}}
\input{appSection8}

>>>>

\section{Proofs from \autoref{section3}: $(\LREL, !_{n})$ is a model of $\BSTLC$}
\input{appSection5}

\section{Proofs from \autoref{sec:tls}: the Analysis of Tropical Power Series}\label{appsec:tls}
\input{app_section4}

\section{Proofs from \autoref{sec:TayLip}: Lipschitz meets Taylor}
\input{appSection7}

\section{Proofs of \autoref{sec:GMS}: $\Lawv$-modules and Generalized Metric Spaces}
\input{appSection8}
